Papers

### 2023-11-28 papers.qmd
minor update

J. Brown, J. P. Davis, **J. D. Tucker**, J. G. Huerta, and K. Shuler, "Quantifying uncertainty in analysis of shockless dynamic compression experiments on platinum, Part 2: Bayesian model calibration", *Journal of Applied Physics*, in revision 2023.

>>>>

J. Brown, J. P. Davis, **J. D. Tucker**, J. G. Huerta, and K. Shuler, "Quantifying uncertainty in analysis of shockless dynamic compression experiments on platinum, Part 2: Bayesian model calibration", *Journal of Applied Physics*, accepted 2023.
